\documentclass[addpoints, 12pt]{exam}
%\documentclass{exam}

\usepackage{amsmath}

\usepackage{multicol}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{calc,arrows,through}
\usetikzlibrary{intersections}

%\usepackage[latin1]{inputenc}
\pagestyle{empty}
\tikzstyle{line} = [draw, -triangle 45]

\pagestyle{head}
\rhead{Name: \rule[-0.1cm]{5cm}{0.01cm}}
\lhead{Financial Literacy - Financial Mathematics\\Section 1-A:  Simple Interest and Simple Discount}

\begin{document}

\begin{questions}

    \question Determine the simple interest payable on a 60-day loan of \$1500 at 14.5\% annual rate
    simple interest.
    \vspace{2in}

    \question Ninety days after borrowing money, you pay back \$850.  How much was originally borrowed
    if you've been charged 9.75\% annual simple interest?
    \vspace{2in}

    \question What is the discounted value of \$1,000 due in 3 months if the simple discount rate is
    11\% annual?
    \vspace{2in}

    \question Mr. Jones owes \$500 due in 4 months and \$700 due in 9 months.  If money is worth
    11\% simple annual interest, what \underline{single} payment \underline{6}  months from now would liquidate his debts?
    \vspace{2in}

    \question You buy a zero-coupon bond with a \$1,000 face amount which will be payable in
    1.5 years.
    If your purchase price was \$892.86, what effective rate of annual simple interest will you earn?
    \vspace{1.5in}

    \question A loan of \$5,000 is repaid after 2 years with a single payment of \$5,500.
    What was the effective
    \begin{itemize}
        \item Annual simple interest rate?
        \item Annual simple discount rate?
    \end{itemize}
    \vspace{1.5in}

    \question Mrs. Johnson has two equivalent options for repaying her loan:
    \begin{itemize}
        \item \$200 at 5 months and \$300 at 10 months, or
        \item \$X after 3 months and \$2X after 6 months.
    \end{itemize}
    What is \$X at 12\% annual simple interest?
    \vspace{1.5in}

    \question You are offered a 3-year loan with your choice of 5\% annual simple interest or
    4.9\% annual simple discount.  Which would you pick, and why?

\end{questions}

\end{document}
