% Financial Mathematics
% Exercise Template
%----------------------------------------------
\documentclass[12pt]{exam}

\pagestyle{head}
\rhead{Name: \rule[-0.1cm]{5cm}{0.01cm}}
\lhead{Financial Literacy - Financial Mathematics\\Section 1-B-2:  Compound Interest (cont.)}

\begin{document}

\vspace{2in}  % doesn't seem to do anything...

\begin{questions}

    \question Parents put \$1,000 into a savings account at the birth of their son.  If the account earns
    interest at 6\% compounded monthly, how much money will be in the account when their son is 18 years old?
    \vspace{1.25in}

    \question Find the annual effective rate equivalent to
    \begin{itemize}
        \item 16\% compounded quarterly?
        \item 18\% compounded monthly
        \item 9.25\% compounded daily
    \end{itemize}
    \vspace{1.5in}

    \question In 1492, Queen Isabella sponsored Christopher Columbus's journey by giving  him the equivalent of \$10,000.
    If she had placed this money in a bank account earning 3\% interest per year, how much would be in the account in 2023?
    \vspace{1.5in}

    \question You can buy a building lot for \$180,000 cash right now, or for payments of \$100,000 now, \$50,000 in 1 year,
    and \$50,000 in 2 years.  Which option is better for you, if money is worth
    \begin{itemize}
        \item 16\% compounded monthly?
        \item 12\% compounded monthly?
    \end{itemize}
    \vspace{2in}

    \question Find the nominal rate compounded quarterly at which \$2,000 will accumulate to \$3,000 in 3 years, 9 months.
    \vspace{2in}

    \question Determine how long it will take for \$100 deposited in an account earning 18\% compounded monthly to
    grow to twice the accumulated value of \$100 deposited at the same time in an account earning 10\% compounded semiannually.
    \vspace{2in}

    \question Joe borrows \$4,000 at a rate of 12\% compounded quarterly.  He promises to pay \$1,000 at the end of one year, \$2,000
    at the end of two years, and the balance at the end of three years.  What is the amount of that final payment?
    \vspace{2in}

    \question What is the value after one year of a deposit of \$1,000 earning 100\% nominal annual interest compounded daily?
    Does that amount of money look familiar to you?

\end{questions}

\end{document}
