% Financial Mathematics
% Exercise Template
%----------------------------------------------
\documentclass[12pt]{exam}

\pagestyle{head}
\rhead{Name: \rule[-0.1cm]{5cm}{0.01cm}}
\lhead{Financial Literacy - Financial Mathematics\\Compound Interest - Additional Practice Problems}

\begin{document}

%\vspace{2in}  % doesn't seem to do anything...

You are trying to decide whether to get a checking account at Bank A or Bank B.  You'll have
paychecks deposited automatically, and you figure you only need to keep about \$300 in
the account to cover routine debit card expenses.
\vspace{.25in}

You have a couple of thousand of dollars in savings, so anything not in a checking account
will be held in a money-market account paying 4\% interest compounded monthly.

\begin{itemize}
    \item Bank A pays no interest, with no requiredd minimum balance, and charges a fee
          of \$1 per month for administration
    \item Bank B pays 1\% interest, compounded monthly, but requires a minimum balance
          of \$1,000 in the checking account at all times.
\end{itemize}

%\vspace{.75in}
\begin{flushleft}
Please answer the following questions.
\end{flushleft}

\begin{questions}

    \question Which checking account would you prefer, and why?
    \vspace{2in}

    \question Let's say you determine that Bank A is preferable.  In order to get
              your business,  Bank B would have to reduce the minimum balance requirement to what amount?
    \vspace{2in}

    \question What if instead Bank B tries to get your business by raising the interest rate. To what rate
              (compounded monthly) would they have to raise their rate?

\end{questions}

\end{document}
