% Financial Mathematics
% Exercise Template
%----------------------------------------------
\documentclass[12pt]{exam}

\pagestyle{head}
\rhead{Name: \rule[-0.1cm]{5cm}{0.01cm}}
\lhead{Financial Literacy - Financial Mathematics\\Section 3-A:  Amortization}

\begin{document}

\vspace{2in}  % doesn't seem to do anything...

\begin{questions}

    \question Joe borrows \$2,000 to be repaid with semiannual payments over 2 years at 12\% compounded
    semiannually.  Construct a complete amortization schedule, showing for each period the total amount of payment,
    the portion going to cover interest, the portion repaying principal, and the outstanding principal remaining.
    \vspace{1.5in}

    \question Barbara borrows \$15,000 to be repaid in equal monthly installments over 4 years at 9\%
    interest compounded monthly.  Find the total amount of interest she will pay over the lifetime
    of the loan.
    \vspace{1.25in}

    \question A loan of \$8,000 is to be amortized with equal monthly payments over 2 years at 15\% compounded
    monthly.  Find the outstanding principal after 7 months, and split the eighth payment into principal
    and interest portions.
    \vspace{2in}

    \question Harold buys a cabin worth \$42,000 by paying \$7,000 down and the balance in monthly installments
    of \$600 for as long as necessary.  If the interest rate is 9\% compounded monthly, find Harold's equity
    in the cabin at the end of 5 years.
    \vspace{2in}

    \question The Smiths borrow \$15,000 to buy a car.  The loan will be repaid over 3 years with monthly payments
    at 6\% compounded monthly.  Find the total interest paid in the 12 payments of the second year of the loan.
    \vspace{2.25in}

    \question The Browns buy a home and assume a \$200,000 mortgage to be amortized with monthly payments over
    15 years at 9\% compounded monthly.  There is no prepayment penalty on their mortgage.  If they can pay an
    extra \$100 per month in addition to the required payment, how long will it take to repay the mortgage, and
    how much will they save in interest paymenmts over the life of the mortgage?
    \vspace{1.5in}

\end{questions}

\end{document}
