% Financial Mathematics
% Exercise Template
%----------------------------------------------
\documentclass[12pt]{exam}

\pagestyle{head}
\rhead{Name: \rule[-0.1cm]{5cm}{0.01cm}}
\lhead{Financial Literacy - Financial Mathematics\\Section 4-A:  Bonds and Stocks}

\begin{document}

\begin{flushleft}
    Do problems 1 through 3 by hand/calculator.  Do the remaining problems using a tool
    like the Excel sheet you can download from Canvas.
\end{flushleft}
\vspace{.5in}

\begin{questions}
    \question You buy a newly-issued, \$1,000, 10 year bond with 7\% annual coupons.  Two years
    later, right after receiving the 2nd coupon, you decide to sell the bond on the secondary market.
    What price will you get if the current annual interest rate is
    \begin{itemize}
        \item 8\% ?
        \item 7\% (still) ?
        \item 6\% ?
    \end{itemize}
    \vspace{1in}
    What relationship do you see between interest rates and bond prices?
    \vspace{.5in}

    \question You buy 100 shares of XYZ Corporation for \$50 a share.  XYZ does  not currently pay
    dividends, and does not expect to for the foreseeable future.  You are hoping to yield 9\%
    annually on your investment.  If you sell your shares in 4 years, what price per share will you
    need to get then in order to have met your investment goal?
    \vspace{1.25in}

    \question You are impressed by the ABC company and its reliable history of annual dividend payments, which
    have been paid at 50 cents per share for the past several years.  If you assume dividends will
    continue at that rate, and that the value of the stock itself will grow 5\% per year, what price
    per share would you pay today if you wanted a 6\% annual return over a 10 year period?
    \vspace{2in}

    \question What is the annual yield on a \$1,000 bond with 5\% annual coupons if you buy it on the secondary
    market, with 4 years until maturity, for a 6\% discount off face value (i.e., for \$940)?
    \vspace{1.5in}

    \question You buy 100 shares of PDQ Corporation for \$50 per share.  It pays no dividend at the end
    of the first year, but it does pay \$1.95 per share at the end of the 2nd, 3rd, and 4th years.  At
    the end of the 5th year, no dividend is payable, and you decide to sell your shares for \$73 per share.
    What was your annual rate of return over the 5 year period?
    \vspace{1.5in}

    \question You have up to \$1,000 to invest.  Your research narrows down your options to these:
    \begin{itemize}
        \item You can buy stock in X Corp.  You don't anticipate earning any dividends.
        \item You can buy a Y Corp bond (on the secondary market) with a \$1,000 face amount that is paying a
        7.7\% annual coupon until maturity, which is 6 years from now.
    \end{itemize}
    The current price of the bond is at a 3\% discount.  Assuming no particular risk or timing requirements, what
    return do you need to expect on the price of the stock in order to make it as attractive as the bond?

\end{questions}

\end{document}